\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-21 draft.tex
emty authors out and different (the math font will be a little more concise then with times)
apply some suggestions from Tomas

\title{\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier}

\hide{
\author{
Yu-Fang Chen\inst{1}\inst{2}
\and
Chang-Yi Chiang\inst{2}
\and
Hsin-Hung Lin\inst{1}
\and
Wei-Tsung Kao\inst{1}
\and
Yean-Fu Wen\inst{2}
\and
Wei-Cheng Wu\inst{1}
}
\institute
{
Institute of Information Science, Academia Sinica, Taiwan
\and
Graduate Institute of Information Management, National Taipei University, Taiwan
}}

@@

In this paper, we propose heuristics for the commutativity problem that works very efficiently on a large set of practical integer reducer programs. We reduce the commutativity problem to an SMT problem in a sound but incomplete manner. We also propose optimizations to enable the approach that works on real-world examples. For the case that the reducer is not proven commutative, we complement the approach by using testing to find concrete counterexamples. We implement all these heuristics as a tool called J-ReCoVer (Java Reducer Commutativity Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|.

We collected benchmarks from open repositories such as Github and Bitbucket to evaluate J-ReCoVer. With the help of a search engine~\cite{searchcode} over those repositories, we collected 118 examples. J-ReCoVer is able to correctly analyze all but 3 of them.

@@

\hide{
\begin{equation*}
\begin{array}{rclcl}
\multicolumn{3}{l}{v\in \Var\mbox{, and }c \in \Z}&&\textmd{Variable and Constant}\\
e \in \Exp    &\ \ \  {\triangleq}\ \ \   & v \mid c \mid \cur \mid e + e \mid e - e \mid e \times e \mid *\mid\ldots & &\textmd{Integer Expression}\\
g\in \Grd  & {\triangleq}  & e < e \mid not\ g \mid g \wedge g  \mid \ldots& & \textmd{Guard}\\
s\in \Cmd  & {\triangleq}  & v:= e \mid out(v) \mid \ite{g}{s}{s} \mid s;s && \textmd{Command}\\
p\in \Prg  & {\triangleq}  & s;\rloop\{s\};s&& \textmd{Reducer Program}\\
\end{array}
\end{equation*}}
\begin{wrapfigure}{r}{3cm}
	\hide{
		\begin{minipage}{0.32\textwidth}
			\begin{algorithm}[H]
				$m := \cur$; \;
				\Loop{}{
					$t:=\cur$;\;
					\uIf{ $t > m$}{
						$m := t$
					}
				};
				$out(m)$\;
			\end{algorithm}
			\caption*{(a) max}
		\end{minipage}
		\hspace{-0.5cm}
	}
	\begin{minipage}{0.3\textwidth}
		\begin{algorithm}[H]
			$s := 0;c:=0$; \;
			\Loop{}{
				$s := s+\cur$;\;
				$c := c+1$
			};
			$o := s/c$;\;
			$out(o)$\;
		\end{algorithm}
	\end{minipage}
	\hide{
		\begin{minipage}{0.4\textwidth}
			\begin{algorithm}[H]
				$a:=*;s := 0; c:=0$;\;
				\Loop{}{
					$s := s+(\cur-a)^2$; \;
					$c := c+1$
				};
				$o := s/c$;\;
				$out(o)$
			\end{algorithm}
			\caption*{(c) standard deviation}
		\end{minipage}
	}
	\caption{Average}
	\label{fig:reducer_example}
\end{wrapfigure}
Let $\Var$ be the set of variables and $\Z$ the set of integers. An \emph{integer expression} in $\Exp$ can be either a variable, constant value, a call to the $\cur$ function that reads and consumes an input value of the reducer, their combinations over basic arithmetic operations, or a non-deterministically chosen integer value $*$.

A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of a sequence of commands, or $out(v)$ that outputs the value of $v$.
A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each \emph{branch}\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing every branch statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g); s_1$ or $(not\ g) ;s_2$. For example, the loop body of Figure~\ref{fig:reducer_example}(a) has two branches $t:=\cur; (t>0); m:=t$ and $t:=\cur;(not\ t>0)$ }. According to our observation over hundreds  of reducer programs in open repositories, reducer programs are almost always in this form. The $\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly until the entire input list is consumed. One example can be found in Figure~\ref{fig:reducer_example}.

\hide{
Some reducer uses two loops to compute the output. For example, for calculating standard deviation, one first computes the average of inputs and then uses it to compute the standard deviation. In that case, we can still verify the reducer by first partitioning it into two reducers and then verifying them separately. One reducer computes the average (Figure~\ref{fig:reducer_example}(b)) and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) (Figure~\ref{fig:reducer_example}(c)). The reducer in Figure~\ref{fig:reducer_example}(c) ``over-approximates''  all possible outputs of the standard deviation computation; it computes an output even if $a$ is not the average of inputs. However, the reducer is still commutative and its commutativity verification can still be done.

In the next section, we give a brief overview of J-ReCoVer,  our tool for reducer commutativity verification.}

@@

\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to further convert it to the so-called ``Jimple'' format, which is an intermediate language that is designed to simplify the analysis of Java programs. Under the Hadoop MapReduce framework, the permutation of the input is handled by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by programmers. In order to deal with this issue, we wrote our own dummy Hadoop environment for the reducer as a part of the Preprocessor component so that the input order of the reducer is now controlled by J-ReCoVer. Finally, we perform in the Preprocessor some program transformation tasks to simplify the analysis. For example, we convert all output commands $out(e)$ inside loops to a special assignment (will be explained in Section~\ref{sec:program_trans1} and~\ref{sec:program_trans2}).

@@

		%JPreprocessor->Technologies
		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1cm] (soot) at (3.2,-2) {};
		\node at (3.2,-2.6) {Soot~\cite{soot}};

@@

		\node at (6.5,-1.6) {
			\begin{minipage}[t]{0.222\textwidth}
			\centering
			Z3 SMT \\
			Solver~\cite{z3}
			\end{minipage}
		};

@@

\textbf{The Prover component} reduces the commutativity problem to an SMT formula satisfiability problem. At a high level, we check equivalence between a reducer program and its variant that has two consecutive inputs swapped. We show that this can be reduced to an SMT problem and give it to the SMT solver Z3~\cite{z3} for solving. In case that Z3 proved the formula unsatisfiable, we know that swapping any two consecutive inputs of the reducer will not change its output. Because all permutations of a list can be obtained by swapping consecutive elements finitely many times, it follows that the reducer outputs the same value for all permutations of the same list of inputs.
In this case,  J-ReCoVer stops and reports that the reducer is commutative.
However, if we run the approach in a naive manner, it does not scale to large programs and is very imprecise.  We will introduce two critical optimizations that enable the proposed approach working for real-world examples in Section~\ref{section:optimizations}: a data flow analysis to extract critical variables and an improved symbolic execution algorithm to generate SMT formulae. More details of the algorithms used in the Preprocessor and the Prover components will be explained in Section~\ref{sec:preprocessor_prover} and the optimizations will be introduced in~\ref{section:optimizations}.

@@

\subsection{The First Program Transformation Task in the Preprocessor}
\label{sec:program_trans1}
J-ReCoVer  first generates a new variable $v_{out_k}$ for the $k$-th output command $out(e)$ inside $s_2$ and replace the $out(e)$ command with an assignment $v_{out_k}:=e$.
Notice that the value of $v_{out_k}$ stays the same from the point it has been assigned a value.
If the values of $v_{out_k}$ are the same for all permutations of input lists at the end of $s_2$, we know that the reducer is commutative w.r.t. to all output values produced inside the loop body $s_2$.

@@

@@

We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to prove the reducer $s_1;\rloop\{s_2\};s_3$ commutative. Notice that $s_1$ does not read from the input (assumed at the beginning of this subsection). The execution of $s_1$ is deterministic in the sense that from the same initial valuation, it outputs the same sequence of values and ends at the same valuation. For the execution of $\rloop\{s_2\}$, from the validity of Equation~(\ref{eq:commu}), any permutation of input values leads the reducer to the same final valuation and the same sequence of outputs at the end of the loop.
Before executing the commands $s_3$, all inputs have been read (the loop exit condition) already. Similar to the case of $s_1$, $s_3$ does not read from the input and hence the execution of $s_3$ is deterministic. It follows that for all permutations of inputs, the reducer outputs the same sequence of values.

@@

\section{Optimization: Live Variable Analysis}
\label{section:optimizations}
In this section, we explain how data flow analysis is used in J-ReCoVer to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in Equation~(\ref{eq:commu}).

We find that in many cases, Equation~(\ref{eq:commu}) is a condition that is too strong for the reducer to be commutative. For instance, consider the example in Figure~\ref{fig:reducer_opt}. In the loop body, the input is first stored in a variable $t$ and then added to $s$. In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of the loop body. Observe that
$F(c_1, F(c_2,s,t)) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t)) = (c_1+c_2, c_2)$. It follows that the corresponding Equation~(\ref{eq:commu}) is invalid. The second component of the returned tuples corresponds to the value of $t$ after executing the loop body twice. Their values are $c_1$ and $c_2$, respectively, in $F(c_1, F(c_2,s,t))$ and $F(c_2, F(c_1,s,t))$. However, in this case, the value of $t$ will not affect the output of this reducer.

\begin{figure}[hbt]
	\begin{minipage}{0.4\textwidth}
		\begin{algorithm}[H]
			$s:= 0$; \;
			\Loop{}{
				$t:=\cur$;
				$s:= s + t$\;
			};
			$out(s)$\;\;\;
		\end{algorithm}
		\caption{A commutative reducer with an invalid Equation~(\ref{eq:commu}).}
		\label{fig:reducer_opt}
	\end{minipage}
	\ \ \ \ \ \ \ \
	\begin{minipage}{0.5\textwidth}
		\LinesNumbered
		\centering
		\begin{minipage}{0.75\textwidth}
		\begin{algorithm}[H]
			$c_1;c_2;\ldots;c_i$\;
			\lIf{$g_1$}{$\ldots$}
			\lElseIf{ $g_2$}{$\ldots$}
			\lElseIf{ $g_3$}{$\ldots$}
			\lElseIf{ $g_m$}{$c_{i+1};\ldots ;c_n; out(v);\ldots$}
			\lElse{ $\ldots$}
		\end{algorithm}
	\end{minipage}
		\caption{The $s_3$ command with an $out(v)$ command in nested branches.}
		\label{fig:nested_out}
	\end{minipage}
\end{figure}

To handle such a situation, we need an algorithm to collect a set of variables whose value may affect the output.
Recall that the first program transformation task uses a set of variables $V_2=\{v_{out_k} \mid k \in [1,l]\}$, where $l$ is the number of output commands occurred in $s_2$, to collect output values occurred in the loop body $s_2$.
The set $V_2$ is exactly the set of variables that will affect the output inside the loop.

@@

However, doing symbolic execution in a naive way can be extremely inefficient.
The length of the formula $val(v)$ can grow exponentially w.r.t. the input commands. For example, consider a simple command $u:=x+y;u:=u+u;u:=u+u$, each execution of $u:= u+ u$ will double the length of the expression representing the symbolic value of $u$. More concretely, after the execution of $u:=x+y$, the symbolic value of $u$ is $x_0+y_0$. After the two executions of $u:=u+u$, the value of $u$ changes to $x_0+y_0+x_0+y_0$ and $x_0+y_0+x_0+y_0+x_0+y_0+x_0+y_0$, respectively. One way to alleviate the problem is to apply formula simplification algorithms, e.g., those implemented in Z3~\cite{z3}.
Here we propose in a very simple alternative solution that works quite well in our reducer benchmarks.

@@

\section{Evaluation}
\label{section:exp}
J-ReCoVer is implemented in Java and built on top of Soot~\cite{soot} 2.5.0 and Z3~\cite{z3} 4.7.1. We run J-ReCoVer on a virtual machine running on a server with AMD Opteron 6376 CPU. 4GB of memory is allocated to this virtual machine. The operation system is Ubuntu 16.04.5 LTS.

In order to properly evaluate the performance of J-ReCoVer, we collect benchmark example from two different sources.
First, we use the search engine \emph{searchcode.com}~\cite{searchcode} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''. Since there is an upper bound on the number of results returned from the search engine, we add different search filters in order to get more data. We tried all $12$ combinations of six filters on code length $\{<50$, $ 50\sim 250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$
and two filters for data sources $\{\url{github.com}, \url{bitbuckect.com}\}$. In total, we get $11346$ Java programs. We exclude cases that are not Hadoop MapReduce reducer programs (those do not import the Hadoop library, do not extend or implement the reducer interface) and obtain $1273$ examples. We further remove those that cannot be compiled, those that are identical to each other, or those with non-numerical data types (e.g, string) and obtained $118$ programs as the final benchmarks.

>>>>

\title{\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier}
\author{}
\institute{}
\hide{
\author{
Yu-Fang Chen\inst{1}\inst{2}
\and
Chang-Yi Chiang\inst{2}
\and
Hsin-Hung Lin\inst{1}
\and
Wei-Tsung Kao\inst{1}
\and
Yean-Fu Wen\inst{2}
\and
Wei-Cheng Wu\inst{1}
}
\institute
{
Institute of Information Science, Academia Sinica, Taiwan
\and
Graduate Institute of Information Management, National Taipei University, Taiwan
}}

@@

In this paper, we propose heuristics for the commutativity problem that works very efficiently on a large set of practical integer reducer programs. We reduce the commutativity problem to an SMT problem in a sound but incomplete manner. We also propose optimizations to enable the approach that works on real-world examples. For the case that the reducer is not proven commutative, we complement the approach by using testing to find concrete counterexamples. We implement all these heuristics as a tool called J-ReCoVer (Java Reducer Commutativity Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|.
We collected benchmarks from open repositories such as Github and Bitbucket to evaluate J-ReCoVer. With the help of a search engine \emph{searchcode.com} over those repositories, we collected 118 examples. J-ReCoVer is able to correctly analyze all but 3 of them.

@@

\hide{
\begin{equation*}
\begin{array}{rclcl}
\multicolumn{3}{l}{v\in \Var\mbox{, and }c \in \Z}&&\textmd{Variable and Constant}\\
e \in \Exp    &\ \ \  {\triangleq}\ \ \   & v \mid c \mid \cur \mid e + e \mid e - e \mid e \times e \mid *\mid\ldots & &\textmd{Integer Expression}\\
g\in \Grd  & {\triangleq}  & e < e \mid not\ g \mid g \wedge g  \mid \ldots& & \textmd{Guard}\\
s\in \Cmd  & {\triangleq}  & v:= e \mid out(v) \mid \ite{g}{s}{s} \mid s;s && \textmd{Command}\\
p\in \Prg  & {\triangleq}  & s;\rloop\{s\};s&& \textmd{Reducer Program}\\
\end{array}
\end{equation*}}
\begin{wrapfigure}{r}{3cm}
		\vspace{-0.8cm}
	\hide{
		\begin{minipage}{0.32\textwidth}
			\begin{algorithm}[H]
				$m := \cur$; \;
				\Loop{}{
					$t:=\cur$;\;
					\uIf{ $t > m$}{
						$m := t$
					}
				};
				$out(m)$\;
			\end{algorithm}
			\caption*{(a) max}
		\end{minipage}
		\hspace{-0.5cm}
	}
	\begin{minipage}{0.3\textwidth}
		\begin{algorithm}[H]
			$s := 0;c:=0$; \;
			\Loop{}{
				$s := s+\cur$;\;
				$c := c+1$
			};
			$o := s/c$;\;
			$out(o)$\;
		\end{algorithm}
	\end{minipage}
	\hide{
		\begin{minipage}{0.4\textwidth}
			\begin{algorithm}[H]
				$a:=*;s := 0; c:=0$;\;
				\Loop{}{
					$s := s+(\cur-a)^2$; \;
					$c := c+1$
				};
				$o := s/c$;\;
				$out(o)$
			\end{algorithm}
			\caption*{(c) standard deviation}
		\end{minipage}
	}
	\caption{Average}
	\vspace{-0.8cm}
	\label{fig:reducer_example}
\end{wrapfigure}
Let $\Var$ be the set of variables and $\Z$ the set of integers. An \emph{integer expression} in $\Exp$ can be either a variable, constant value, a call to the $\cur$ function that reads and consumes an input value of the reducer, their combinations over basic arithmetic operations, or a non-deterministically chosen integer value $*$.
A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of a sequence of commands, or $out(v)$ that outputs the value of $v$.
A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each \emph{branch}\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing every branch statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g); s_1$ or $(not\ g) ;s_2$. For example, the loop body of Figure~\ref{fig:reducer_example}(a) has two branches $t:=\cur; (t>0); m:=t$ and $t:=\cur;(not\ t>0)$ }. According to our observation over hundreds  of reducer programs in open repositories, reducer programs are almost always in this form. The $\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly until the entire input list is consumed. One example can be found in Figure~\ref{fig:reducer_example}.

Some reducer uses two loops to compute the output. For example, for calculating standard deviation, one first computes the average of inputs and then uses it to compute the standard deviation. In that case, we can still verify the reducer by first partitioning it into two reducers and then verifying them separately. One reducer computes the average and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) that will be used in standard deivation. The second reducer ``over-approximates''  all possible outputs of the standard deviation computation; it computes an output even if $a$ is not the average of inputs. However, this reducer is still commutative and its commutativity verification can still be done.

@@

\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot to further convert it to the so-called ``Jimple'' format, which is an intermediate language that is designed to simplify the analysis of Java programs. Under the Hadoop MapReduce framework, the permutation of the input is handled by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by programmers. In order to deal with this issue, we wrote our own dummy Hadoop environment for the reducer as a part of the Preprocessor component so that the input order of the reducer is now controlled by J-ReCoVer. Finally, we perform in the Preprocessor some program transformation tasks to simplify the analysis. For example, we convert all output commands $out(e)$ inside loops to a special assignment (will be explained in Section~\ref{sec:program_trans1} and~\ref{sec:program_trans2}).

@@

		%JPreprocessor->Technologies
		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1cm] (soot) at (3.2,-2) {};
		\node at (3.2,-2.6) {Soot};

@@

		\node at (6.5,-1.6) {
			\begin{minipage}[t]{0.222\textwidth}
			\centering
			Z3 SMT \\
			Solver
			\end{minipage}
		};

@@

\textbf{The Prover component} reduces the commutativity problem to an SMT formula satisfiability problem. At a high level, we check equivalence between a reducer program and its variant that has two consecutive inputs swapped. We show that this can be reduced to an SMT problem and give it to the SMT solver Z3 for solving. In case that Z3 proved the formula unsatisfiable, we know that swapping any two consecutive inputs of the reducer will not change its output. Because all permutations of a list can be obtained by swapping consecutive elements finitely many times, it follows that the reducer outputs the same value for all permutations of the same list of inputs.
In this case,  J-ReCoVer stops and reports that the reducer is commutative.
However, if we run the approach in a naive manner, it does not scale to large programs and is very imprecise.  We will introduce two critical optimizations that enable the proposed approach working for real-world examples in Section~\ref{section:optimizations}: a data flow analysis to extract critical variables and an improved symbolic execution algorithm to generate SMT formulae. More details of the algorithms used in the Preprocessor and the Prover components will be explained in Section~\ref{sec:preprocessor_prover} and the optimizations will be introduced in~\ref{section:optimizations}.

@@

\subsection{The First Program Transformation Task in the Preprocessor}
\label{sec:program_trans1}
Recall that the reducer program can perform the ouput command $out(e)$ inside the loop body $s_2$. In this case, we remember the output value in a fresh variable $v$ and replace the $out(e)$ command with an assignment $v:=e$.
Notice that the value of $v$ stays the same from the point it has been assigned a value.
If the values of $v$ are the same for all permutations of input lists at the end of $s_2$, we know that the reducer is commutative w.r.t. to all output values produced inside the loop body $s_2$.

@@

\hide{

@@

We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to prove the reducer $s_1;\rloop\{s_2\};s_3$ commutative. Notice that $s_1$ does not read from the input (assumed at the beginning of this subsection). The execution of $s_1$ is deterministic in the sense that from the same initial valuation, it outputs the same sequence of values and ends at the same valuation. For the execution of $\rloop\{s_2\}$, from the validity of Equation~(\ref{eq:commu}), any permutation of input values leads the reducer to the same final valuation and the same sequence of outputs at the end of the loop.
Before executing the commands $s_3$, all inputs have been read (the loop exit condition) already. Similar to the case of $s_1$, $s_3$ does not read from the input and hence the execution of $s_3$ is deterministic. It follows that for all permutations of inputs, the reducer outputs the same sequence of values.}

@@

\subsection{Optimization: Live Variable Analysis}
\label{section:optimizations}
In this section, we explain how data flow analysis is used in J-ReCoVer to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in Equation~(\ref{eq:commu}).

We find that in many cases, Equation~(\ref{eq:commu}) is a condition that is too strong for the reducer to be commutative. For instance, consider a simple example. In the loop body, the input is first stored in a variable $t$ and then added to $s$. After the loop, output the value of $s$.
In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of the loop body. Observe that
$F(c_1, F(c_2,s,t)) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t)) = (c_1+c_2, c_2)$. It follows that the corresponding Equation~(\ref{eq:commu}) is invalid. The second component of the returned tuples corresponds to the value of $t$ after executing the loop body twice. Their values are $c_1$ and $c_2$, respectively, in $F(c_1, F(c_2,s,t))$ and $F(c_2, F(c_1,s,t))$. However, in this case, the value of $t$ will not affect the output of this reducer.

\hide{
\begin{figure}[hbt]
	\begin{minipage}{0.4\textwidth}
		\begin{algorithm}[H]
			$s:= 0$; \;
			\Loop{}{
				$t:=\cur$;
				$s:= s + t$\;
			};
			$out(s)$\;\;\;
		\end{algorithm}
		\caption{A commutative reducer with an invalid Equation~(\ref{eq:commu}).}
		\label{fig:reducer_opt}
	\end{minipage}
	\ \ \ \ \ \ \ \
	\begin{minipage}{0.5\textwidth}
		\LinesNumbered
		\centering
		\begin{minipage}{0.75\textwidth}
		\begin{algorithm}[H]
			$c_1;c_2;\ldots;c_i$\;
			\lIf{$g_1$}{$\ldots$}
			\lElseIf{ $g_2$}{$\ldots$}
			\lElseIf{ $g_3$}{$\ldots$}
			\lElseIf{ $g_m$}{$c_{i+1};\ldots ;c_n; out(v);\ldots$}
			\lElse{ $\ldots$}
		\end{algorithm}
	\end{minipage}
		\caption{The $s_3$ command with an $out(v)$ command in nested branches.}
		\label{fig:nested_out}
	\end{minipage}
\end{figure}

To handle such a situation, we need an algorithm to collect a set of variables whose value may affect the output.
Recall that the first program transformation task uses a set of variables $V_2=\{v_{out_k} \mid k \in [1,l]\}$, where $l$ is the number of output commands occurred in $s_2$, to collect output values occurred in the loop body $s_2$.
The set $V_2$ is exactly the set of variables that will affect the output inside the loop.}

@@

However, doing symbolic execution in a naive way can be extremely inefficient.
The length of the formula $val(v)$ can grow exponentially w.r.t. the input commands. For example, consider a simple command $u:=x+y;u:=u+u;u:=u+u$, each execution of $u:= u+ u$ will double the length of the expression representing the symbolic value of $u$. More concretely, after the execution of $u:=x+y$, the symbolic value of $u$ is $x_0+y_0$. After the two executions of $u:=u+u$, the value of $u$ changes to $x_0+y_0+x_0+y_0$ and $x_0+y_0+x_0+y_0+x_0+y_0+x_0+y_0$, respectively. One way to alleviate the problem is to apply formula simplification algorithms, e.g., those implemented in Z3.
Here we propose in a very simple alternative solution that works quite well in our reducer benchmarks.

@@

\section{Evaluation}
\label{section:exp}
J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1. We run J-ReCoVer on a virtual machine running on a server with AMD Opteron 6376 CPU. 4GB of memory is allocated to this virtual machine. The operation system is Ubuntu 16.04.5 LTS.

In order to properly evaluate the performance of J-ReCoVer, we collect benchmark example from two different sources.
First, we use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''. Since there is an upper bound on the number of results returned from the search engine, we add different search filters in order to get more data. We tried all $12$ combinations of six filters on code length $\{<50$, $ 50\sim 250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$
and two filters for data sources $\{\url{github.com}, \url{bitbuckect.com}\}$. In total, we get $11346$ Java programs. We exclude cases that are not Hadoop MapReduce reducer programs (those do not import the Hadoop library, do not extend or implement the reducer interface) and obtain $1273$ examples. We further remove those that cannot be compiled, those that are identical to each other, or those with non-numerical data types (e.g, string) and obtained $118$ programs as the final benchmarks.
